---
title: "EHD_Analysis"
author: "Chrissy_casey"
date: "January 6, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)

HD<-read.csv("C:/Users/Chrysalis/Documents/clcasey/EHD/workingEHD.csv")

#Binary Multiple Logistic Regression 
# x = physiographic region: Appalachian Plateaus - yes(1), no(0)
# y = EHD presence(1) or absence(0)

#Removing empty columns
HD$X.1<-NULL
HD$X.2<-NULL

#Converting all data to numeric

HD$AP_status = as.numeric(HD$AP_status)
HD$EHD_status = as.numeric(HD$EHD_status)

colnames(HD)[colnames(HD)=="ï..State"] <- "state"

y_hd<-HD$EHD_status
x_ap<-HD$AP_status

model1<-glm(y_ehd~x_ap,binomial)
summary(model1)# see below

OR<-exp(coef(model1))
OR
#OR<-exp(1.40841)
#OR = 4.089448  EHD is 4 times more likely to occur in Appalachian Plateaus than not in the Appalachian Plateaus

CI<-exp(confint.default(model1))
CI
#                2.5 %    97.5 %
# x_ap        3.0983162 5.3976011

anova(model1, test="Chisq")

```
Call:
glm(formula = y_ehd ~ x_ap, family = binomial)

Deviance Residuals: 
    Min       1Q   Median       3Q      Max  
-1.2789  -0.7343  -0.7343   1.0792   1.6986  

Coefficients:
            Estimate Std. Error z value Pr(>|z|)    
(Intercept) -1.17295    0.06489 -18.077   <2e-16 ***
x_ap         1.40841    0.14161   9.946   <2e-16 ***
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

(Dispersion parameter for binomial family taken to be 1)

    Null deviance: 1889.8  on 1571  degrees of freedom
Residual deviance: 1790.6  on 1570  degrees of freedom
AIC: 1794.6

Number of Fisher Scoring iterations: 4

Analysis of Deviance Table

Model: binomial, link: logit

Response: y_ehd

Terms added sequentially (first to last)


     Df Deviance Resid. Df Resid. Dev  Pr(>Chi)    
NULL                  1571     1889.8              
x_ap  1   99.233      1570     1790.5 < 2.2e-16 ***
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1


```{r}
library(ggplot2)
library(msm)
library(sandwich)

PGR<-as.factor(HD$PGR_Major)
PGR.f<-HD$PGR_Major


model2<-glm(y_hd~PGR)
summary(model2)

#model2: significant physiogeographic region: Appalachian Plateaus, Blue Ridge, Rigde and Valley


minmodelAP<-glm(HD$HD_min~HD$AP_status)
summary(minmodelAP)

minmodelALL<-glm(HD$HD_min~PGR)
summary(minmodelALL)



```
summary(PGR)
PHYSGEO REG:  1   2   4   6   7  11  14  17  19  22  23  24 
Num counties  7 210  41 352 435 145  64   1 183   4  28 102 

1 = adirondack
2 = Appalachian Plateaus
4 = Blue Ridge 
6 = Central Lowland
7 = Coastal Plain
11 = Interior Low Plataues
14 = New England
17 = Ozark Plateaus
19 = Piedmont
22= St. Lawrence Valley
23= Superior Upland
24= Valley & Ridge

#Summary for Model based on physiogeographic Region and all HD report
glm(formula = y_hd ~ PGR)

Deviance Residuals: 
    Min       1Q   Median       3Q      Max  
-0.5769  -0.1935  -0.1643   0.4231   0.9219  

Coefficients:
              Estimate Std. Error t value Pr(>|t|)    
(Intercept) -1.546e-15  1.499e-01   0.000 1.000000    
PGR2         5.769e-01  1.528e-01   3.777 0.000165 *** #  SIGNIFIGANT
PGR4         4.390e-01  1.639e-01   2.679 0.007463 **  #  SIGNIFIGANT
PGR6         1.643e-01  1.516e-01   1.084 0.278595    
PGR7         1.935e-01  1.513e-01   1.279 0.200944    
PGR11        3.239e-01  1.581e-01   2.049 0.040662 *   #  SIGNIFIGANT
PGR14        7.812e-02  1.590e-01   0.491 0.623242    
PGR17        1.000e+00  4.497e-01   2.224 0.026316 *   #  SIGNIFIGANT
PGR19        3.043e-01  1.531e-01   1.988 0.047038 *   #  SIGNIFIGANT
PGR22       -4.086e-15  2.596e-01   0.000 1.000000    
PGR23        9.149e-16  1.707e-01   0.000 1.000000    
PGR24        5.028e-01  1.533e-01   3.281 0.001057 **  #  SIGNIFIGANT
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

(Dispersion parameter for gaussian family taken to be 0.179771)

    Null deviance: 322.88  on 1571  degrees of freedom
Residual deviance: 280.44  on 1560  degrees of freedom
AIC: 1777.4

#Summary of model with HD reports excluding criteria 4 and just AP_status
Call:
glm(formula = HD$HD_min ~ HD$AP_status)

Deviance Residuals: 
    Min       1Q   Median       3Q      Max  
-0.5430  -0.1991  -0.1991   0.4570   0.8009  

Coefficients:
             Estimate Std. Error t value Pr(>|t|)    
(Intercept)    0.1991     0.0115   17.31   <2e-16 ***
HD$AP_status   0.3439     0.0285   12.06   <2e-16 ***
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

(Dispersion parameter for gaussian family taken to be 0.1741186)

    Null deviance: 298.71  on 1571  degrees of freedom
Residual deviance: 273.37  on 1570  degrees of freedom
AIC: 1717.3

Number of Fisher Scoring iterations: 2


```{r}
library(usmap)
library(ggplot2)

plot_usmap(data=HD, values = "EHD_status", regions = "counties", include = c("FL", "GA", "AL", "SC", "VA","NC","MS","NC","TN","KY","IN","IL","WV","MD","MA","ME","MI","NH","RI","VT","DE","CT","NJ","NY","PA","OH","WI"), lines = "black")+ 
  scale_fill_continuous(low = "white", high = "red", name = "HD Reported", label = scales::comma) + 
  theme(legend.position = "right") + labs(title = "HD Reports by County in Eastern US States, 2017")
```

```{r}

HD$PGR_Major=as.factor(HD$PGR_Major)

colors <- c("maroon", "darkgreen", "blue", "yellow", "darkorange1", "purple", "mediumspringgreen","magenta","cyan","gold","lightsteelblue","red")
names(colors) = c("Adirondack", "Appalachian_Plateaus", "Blue_Ridge", "Central_Lowland","Coastal_Plain","Interior_Low_Plateaus","New_England","Ozark_Plateaus","Piedmont","StLawrence_Valley","Superior_Upland","Ridge_Valley")

plot_usmap(data=HD, values = "PGR_Major", regions = "counties", include = c("FL", "GA", "AL", "SC", "VA","NC","MS","NC","TN","KY","IN","IL","WV","MD","MA","ME","MI","NH","RI","VT","DE","CT","NJ","NY","PA","OH","WI"), lines = "black")+ scale_fill_manual(values=colors)+theme(legend.position = "right")

```
```{r}
library(ggplot2)
library(maps)

# Load the county data from the maps package
eastUS <- map_data("county","alabama")

# Plot the counties
#ggplot(cnty, aes(long,lat, group = group)) + 
#  geom_polygon(aes(fill = region), colour = rgb(1,1,1,0.2)) + 
#  theme(legend.position="none") +
#  coord_quickmap()
```

```{r}

### Test for correlation examples NEED to edit to make working code
#library(PerformanceAnalytics)

#chart.Correlation(workingEHD, 
#                  method="spearman",
#                  histogram=TRUE,
#                  pch=16)

#library(psych)

#corr.test(workingEHD, 
#          use = "pairwise",
#          method="spearman",
#          adjust="none",      
#          alpha=.05)

#TESTING regression examples models
#model.null = glm(Status ~ 1, 
#                 data=Data.omit,
#                 family = binomial(link="logit")
#                 )

#model.full = glm(Status ~ Length + Mass + Range + Migr + Insect + Diet + Clutch + Broods + Wood + Upland + Water + Release + Indiv,
#                 data=Data.omit,
#                 family = binomial(link="logit")
#                 )
     
#step(model.null,
#     scope = list(upper=model.full),
#             direction="both",
#             test="Chisq",
#             data=Data)
```

```{r}
#UTM coordinates 
#df <- data.frame(workingEHD$Lat, workingEHD$Long)
#df$X <- df$workingEHD.Long
#df$Y <- df$workingEHD.Lat
#df <- df[-c(1,2)]
#df

#LongLatToUTM<-function(x,y,zone){
# xy <- data.frame(ID = 1:length(x), X = x, Y = y)
#  coordinates(xy) <- c("X", "Y")
#  proj4string(xy) <- CRS("+proj=longlat +datum=WGS84")  ## for example
#  res <- spTransform(xy, CRS(paste("+proj=utm +zone=",zone," ellps=WGS84",sep='')))
#  return(as.data.frame(res))
#}

# new.df <- LongLatToUTM(x=df$X, y=df$Y, 16)# How can I make it include more than one zone?
```
